---
title: "theoryCalc"
author: "Alex Holcombe"
date: ""
output: html_document
---
```{r}

#setwd(
#  "/Users/alexh/Documents/attention_tempresltn/multiple object tracking/newTraj/newTraj_repo/analysis"
#)
library(ggplot2)
```

What does rps limit imply for cortical magnification factor?
Constant rps limit implies receptive fields must be 6.28 deg (2pi) farther apart for every unit increase in eccentricity. 
A unit distance on cortex is assumed to be a constant number of receptive fields (this is the logic of measuring "perceptive field" size).

Whatever that number of receptive fields is, it should span 6.28 deg visual angle more for every unit increase in eccentricity.
What does this correspond to in terms of cortical magnification factor? M inverse, because
M was initially defined as the cortical distance in cortex onto which 1 deg of visual field projects, whereas
Minv, M inverse, is the visual angle for a particular cortical distance.

deg/RF (degrees per every two receptive fields) = Minv * mm/RF
So if mm/RF = .01, I'm interested in Minv*.01, specifically how much it increases per deg eccentricity. According to rps limit, that's 6.28. So that seems a huge increase given how little Minv increases (see below)


From Strasburger et al. (2011, JoV):
Minv = MfovealInverse * (1 + aE)  

Looking at Figure 9 of Strasburger et al. (2011), they plot several example graphs, and the slopes for r= -> r= are

Study |          1/M for r=4.5 | for r=12     |  diff of Minv            
------------- | ------------- | ------------- | ------------- 
Schira et al.() |  `r s1Inv=0.26; s1Inv` | `r s2Inv=0.69; s2Inv` | `r sDiff=s2Inv-s1Inv; sDiff`
Van Essen et al. | `r v1Inv=0.53; v1Inv` | `r v2Inv=1.27; v2Inv` | `r vDiff=v2Inv-v1Inv; vDiff`

So cortical distance in deg/mm cortex according to Schira increases by only `r sDiff` for the increase of my experiment of r of `r 12-4.5`.

Yet for rps to be constant we need a `r round( (12-4.5)*2*pi ,2) ` increase in deg/mm.

But how many mm of cortex are we talking about- does that matter? Let's say receptive fields are spaced 0.1 mm apart.
Then increase in deg is `r .43*.1`

In fact the rps limit found in the present paper did change slightly from r=4.5 to r=12, namely it decrased by 0.38 rps for the CRT and 0.39 rps for the Spinzter.

```{r}

calcMeanEccentricityAlongCircle <- function(radius,eccentricity,epsilonTheta) {
  #numerically integrate as at https://github.com/alexholcombe/MOTcircular/blob/master/analysis/theory.md
  #for each theta of the circle, calculate distance from origin to that point
  r = radius
  e = eccentricity
  thetas = seq(from=0,to=2*pi-epsilonTheta,by=epsilonTheta)
  
  #imagine the center is at e,0
  #For each theta, calculate the point's coordinates. Then square its x and y, square root of that
  squares = (e + r*cos(thetas))^2 + (r*sin(thetas))^2
  sumOfEccentricities = sum( sqrt(squares) )
  avgEccentricity = sumOfEccentricities / length(thetas)
    
  return (avgEccentricity)
}

#Test function
calcMeanEccentricityAlongCircle(5, 0, .01)  #Should equal 5
calcMeanEccentricityAlongCircle(3, 10, .001)  #Should equal 10, but get 10.22621. Maybe that's the right answer!
calcMeanEccentricityAlongCircle(2.5, 2, .001)  #2.92
calcMeanEccentricityAlongCircle(3.5, 3, .001)  #4.18
calcMeanEccentricityAlongCircle(6, 5, .001)  #7.1 That's 

#Calc predictions for my experiment
r=6
exp<-data.frame(ecc=c(5,10),meanAlong=NaN)
exp$meanAlong[1] = calcMeanEccentricityAlongCircle(r, exp$ecc[1], .001)
exp$meanAlong[2] = calcMeanEccentricityAlongCircle(r, exp$ecc[2], .001)
exp$predictedRatio = exp$meanAlong/r
#An 18% boost and 82% in speed limit predicted.

#Calculate in a different direction to make sure I'm right. See https://github.com/alexholcombe/MOTcircular/blob/master/experiment_specific/rps_limit/theory.md
speedLimDva <- function(x,e) {
	#x is limit in revolutions per second
	#e is eccentricity
	dvaPerSecond = 2*pi*x*e
	return (dvaPerSecond)
}

exampleRpsLimit = 1 #by using 1, the increase will show the ratio
exp$dvaPerSec = speedLimDva(exampleRpsLimit,exp$meanAlong)
exp$rps = exp$dvaPerSec / (2*pi*6)
exp

#Check that both ways of doing the calculation give the same answer
if (sum(exp$rps - exp$speedUp) < .00001) {
	cat("Both ways of calculating coincide")
} else {
	cat("The ways of calculating do not coincide")
}

```

